---
title: "Homework 1"
author: Rio Yan
output: github_document
---

This is my solution to HW1. 

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Try converting logical vector and multiply the random sample.
```{r try_factor_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2

Load the penguins dataset.

```{r load_data}
data("penguins", package = "palmerpenguins")
```

The penguins dataset collected `r ncol(penguins)` variables and they are `r names(penguins)`.

The sample size of the dataset is `r nrow(penguins)` penguins.

There are three penguin species in the dataset: `r levels(pull(penguins, "species"))`, and the data is collected from three islands: `r levels(pull(penguins, "island"))`.


The bill length ranges from `r min(pull(penguins, bill_length_mm), na.rm = TRUE)`mm to `r max(pull(penguins, bill_length_mm), na.rm = TRUE)`mm. 
The bill depth ranges from `r min(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm to `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm. 
The flipper length ranges from `r min(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm to `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm. 
The body mass ranges from `r min(pull(penguins, body_mass_g), na.rm = TRUE)`g to `r max(pull(penguins, body_mass_g), na.rm = TRUE)`g.
The data was collected from `r min(pull(penguins, year), na.rm = TRUE)` to `r max(pull(penguins, year), na.rm = TRUE)`.


The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length of the penguins in the dataset is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.




Make the scatterplot.

```{r plot_scatter}

ggplot(penguins, aes(bill_length_mm, flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)

```

